---
title: "Boston Crime Data EDA"
author: "Joseph Sepich"
date: "2019-07-31"
output: 
  html_document:
    keep_md: yes
  html_notebook: default
---

# Front matter

```{r message = FALSE, warning = FALSE}
# always clean up R environment
rm(list = ls())
# load all packages here
library(mdsr) # book package of utilities
library(tidyr) # tidyverse utilities
library(lubridate) # date utility package
library(data.table) # using fread function
library(tidyverse) # utitlity package
```

# Obtaining the data

## Import data

```{r}
crime_data <- fread("Data/tmpney_to1g.csv")
offense_codes <- fread("Data/crimes-in-boston/offense_codes.csv")
```

```{r}
head(crime_data)
```

```{r}
str(crime_data)
```

```{r}
str(offense_codes)
```

The cases of the csv are in a tidy format, but we can combine the information stored in the csv. We can also convert some data types. For instance the OCCURRED_ON_DATE field contains all the information regarding time data. We can transform this into a date time field. One question to answer after that is if shooting is a boolean type field or not.

## Remove redundant columns

Let's consolidate our time fields and our location information.

```{r}
crime_data_tidy <- crime_data %>%
  select(-c(YEAR,MONTH,DAY_OF_WEEK,HOUR,Location))

str(crime_data_tidy)
```

```{r}
crime_data_tidy %>%
  write.csv("Data/tidy_crimes.csv")
```

## Cast types

Now let's convert the OCCURRED_ON_DATE field to a date field.

```{r}
crime_data_tidy$OCCURRED_ON_DATE <- ymd_hms(crime_data_tidy$OCCURRED_ON_DATE)

str(crime_data_tidy$OCCURRED_ON_DATE)
```














