---
title: "Time Tracking EDA"
author: "Joseph Sepich"
date: "2019-10-16"
output: 
  html_notebook: default
  html_document:
    keep_md: yes
---

# Background

I have begun tracking how I spend my time. I can export those records into a relational table that are imported here. What can I discover about my time management? How much time do I allocate to work compared to leisure? Let's find out.

```{r echo=FALSE}
# import packages
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
```

# Inspect data

```{r}
time_table <- fread("./Data/time_data_11_14.csv")
```

```{r}
str(time_table)
```

```{r}
head(time_table, 10)
```

```{r}
tail(time_table, 10)
```

# Overall Time Spent


## Time spent per Task

```{r}
time_table %>%
  group_by(Task, Project) %>%
  summarise(total_duration = sum(`Decimal Duration`)) %>%
  ggplot(aes(x=reorder(Task, total_duration),y=total_duration,fill=Project)) +
    geom_bar(stat='identity') +
    coord_flip() +
    xlab('Task Name') +
    ylab('Duration in Hours') +
    ggtitle('Total Task Duration')
```

## Time spent per Project

```{r}
time_table %>%
  group_by(Project) %>%
  summarise(total_duration = sum(`Decimal Duration`)) %>%
  ggplot(aes(x=reorder(Project, total_duration),y=total_duration)) +
    geom_bar(stat='identity') +
    coord_flip() +
    xlab('Project Name') +
    ylab('Duration in Hours') +
    ggtitle('Total Project Duration')
```

# Projecct times

### Convert dates

```{r}
time_data <- time_table

time_data$Start <- ymd_hm(time_table$Start)
time_data$End <-ymd_hm(time_table$End)

time_data$StartHour <- hour(time_table$Start)
time_data$StartDay <- yday(time_table$Start)
time_data$StartWeekDay <- wday(time_table$Start, TRUE)
time_data$StartHourMinute <- minute(time_table$Start)
str(time_data)
```

## Density through year

```{r}
time_data %>%
  ggplot(aes(x=StartDay, color=Task)) +
    geom_density() +
    facet_wrap(.~Project) +
    xlab('Day of Year') +
    ylab('Density') +
    ggtitle('Frequency of Project by Day')
```

## Density through day

```{r}
time_data %>%
  ggplot(aes(x=StartHour, color=Task)) +
    geom_density() +
    facet_wrap(.~Project) +
    xlab('Hour of Day') +
    ylab('Density') +
    ggtitle('Frequency of Project by Hour')
```

### Personal Project

```{r}
time_data %>%
  filter(Project=="Personal") %>%
  ggplot(aes(x=StartHour, color=Task)) +
    geom_density() +
    xlab('Hour of Day') +
    ylab('Density') +
    ggtitle('Frequency of Project by Hour')
```

## Work Hours

I want to know roughly how much I work in a week. Do I work more, less, or the same as a full time employee? How does my productivity shift throughout a single week?

```{r}
time_data$StartWeek <- week(time_table$Start)
```

```{r}
working_data <- time_data %>%
  filter(Project %in% c("SchoolWork","Work")) %>%
  group_by(StartWeek) %>%
  summarise(totalHours=sum(`Decimal Duration`))
```

```{r}
working_data

mean(working_data$totalHours)
```

```{r}
time_data %>%
  filter(Project %in% c("SchoolWork","Work")) %>%
  group_by(StartWeekDay) %>%
  summarise(totalHours=mean(`Decimal Duration`)) %>%
  ggplot(aes(x=StartWeekDay,y=totalHours)) +
  geom_point()
```







